A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-08-11 papers/water-SAFT/paper.tex
next edit of walther-referencing paragraph Tested everything on kipu.

Walther \emph{et al.}\cite{walther2004hydrophobic} studied the
interactions between two carbon nanotubes, which are geometrically
similar to our hydrophobic rods, by using molecular dynamics with
Lennard-Jones potentials for nanotubes of diameter 1.25~nm and
separations ranging from about 0.3~nm to 1.5~nm. They compute the
force to constrain the nanotubes at different sepearation distances
and find that a drying transition begins at separations near 0.9~-~1.0~nm where two
layers of water molecules can exist in a metastable state between the
rods. This reduces to one layer at a spacing of 0.55~-~0.58~nm, and at
0.35~nm water is complete expelled and is in
equilibrium\cite{walther2004hydrophobic}. The final drying state is
smaller than what we find for hydrophobic rods of a similar size, as
expected due to the carbon-water interaction and the
van der Waals interaction between the rods that causes more attraction
than our rods.  Our model does not predict any of the transitional
states seen here\fixme{why?}.

>>>>

Walther \emph{et al}\cite{walther2004hydrophobic} studied the
interactions between two carbon nanotubes, which are geometrically
similar to our hydrophobic rods, using molecular dynamics with the SPC
model for water, and a Lennard-Jones potential for the interaction of
carbon with water, for nanotubes of diameter 1.25~nm and separations
ranging from about 0.3~nm to 1.5~nm.  The SPC model underestimates the
surface tension of water by about 24\%\cite{vega2007surface}, so we
cannot expect this work to provide quantitative agreement with real
water.  Walther \emph{et al} observe a drying transition between the
two nanotubes, which occurs at a smaller radius than our results
suggest.  However, when Walther \emph{et al} disable the attractive
interaction between nanotube and water, the drying effect occurs at
much longer range, in agreement with our results.  \fixme{Please read
  this carefully, as I did some major changes.  I took a look at the
  paper, and it seems that in Figure 3c (and the paragraph that ends
  at the top of that page) they finally do a truly hydrophobic
  interaction, which is a better comparison with what we did.  The
  drying transition is inhibited by the attraction between tube and
  water. }
